---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FlowCodeUnmixRcpp

<!-- badges: start -->
<!-- badges: end -->

The goal of FlowCodeUnmixRcpp is to speed up the unmixing of FlowCode-barcoded spectral flow cytometry data. It is an add-on package to `FlowCodeUnmix` using fast per-cell unmixing in C++.

## Installation

You will need [Rtools](https://cran.r-project.org/bin/windows/Rtools/) (on Windows) or [Xcode command line tools](https://teuder.github.io/rcpp4everyone_en/020_install.html) (on Mac). Install this first.

You can install the development version of FlowCodeUnmixRcpp like so:

``` {r, eval=FALSE}
remotes::install_github("DrCytometer/FlowCodeUnmixRcpp")
```

You will need [AutoSpectral](https://github.com/DrCytometer/AutoSpectral), [FlowCodeUnmix](https://github.com/DrCytometer/FlowCodeUnmix) and their dependencies for full functionality.

``` {r, eval=FALSE}
# Install Bioconductor packages
if (!requireNamespace("BiocManager", quietly = TRUE))
  install.packages("BiocManager")
BiocManager::install(c("flowWorkspace", "flowCore", "PeacoQC", "FlowSOM"))

# You'll need devtools or remotes to install from GitHub.
# install.packages("devtools")
remotes::install_github("DrCytometer/AutoSpectral")
remotes::install_github("DrCytometer/FlowCodeUnmix")
```

See [AutoSpectral](https://drcytometer.github.io/AutoSpectral/index.html) and `FlowCodeUnmix` for workflow and instructions.
